Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-21 paper.qmd
Update the plots

sc_ltr_pos <- c(0.08, 0.96)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 2.59)
nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)
```

>>>>

sc_ltr_pos <- c(0.08, 0.96)
# sc_xlims <- c(-0.25, 1.25)
# sc_ylims <- c(-0.25, 2.59)
sc_xlims <- c(-0.25, 1.25)
sc_ylims <- c(-0.25, 1.8)

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)
```
